Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-05-22 main.tex
:art: Refactor code

		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.

@@

\begin{section}{Metascatter}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{metascatter_system.eps_tex}
			\caption{The proposed Metascatter system.}
			\label{fi:metascatter_system}
		\end{figure}
		As shown in Fig. \ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
		\begin{footnote}
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		\end{footnote}

@@

		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
			\label{eq:primary_marginal_information_function}
		\end{equation}
		and the primary (ergodic) mutual information is
		\begin{equation}
			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			\label{eq:primary_mutual_information}
		\end{equation}

>>>>

		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.

@@

\begin{section}{Metascatter}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{metascatter_system.eps_tex}
			\caption{The proposed Metascatter system.}
			\label{fi:metascatter_system}
		\end{figure}
		As shown in Fig. \ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol length is $N \in \mathbb{Z}_{++}$ times the primary symbol length.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
		\begin{footnote}
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		\end{footnote}

@@

		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
		% TODO notation
		\begin{equation}
			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
			\label{eq:primary_marginal_information_function}
		\end{equation}
		and the primary (ergodic) mutual information is
		\begin{equation}
			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			\label{eq:primary_mutual_information}
		\end{equation}
